---
title: Pathogens & global change figure report
author: Cole B. Brookson
output: html_document
---

## Accompanying information 

This document contains a brief run-down of all the analysis-related figures in the main text of the pathogens & planetary change manuscript referenced in the root README. 

### Figure 1 

Figure 1 is the figure involving the most data generated in other publications. For details on how it was created, see `./data/recreation/README.md` or Text S2 in the main text of the manuscript. 

```{r}
library(here)
source(here::here("./src/fig1/hockeystick-map-generation.R"))
all_panels + patchwork::plot_annotation(
    caption = paste0(
        "Spillover events of high-consequence zoonotic diseases
        follow an upward trend similar to the “hockey stick” trends of
        iodiversity loss and climate change; however, there is less consensus
        that the observed trend in spillover rates is independent of
        improvements in outbreak detection. Novel human infectious diseases
        emerge more often in regions of the world with higher mammal
        biodiversity, but are also more likely to be detected by surveillance
        systems and described for the first time in Europe and North America.
        For a full explanation of data sources, see Text S2 in the main paper."
    )
)
```

### Figure 4 

Figure 4 is based on data from GBIF exclusively. 

```{r}
source(here::here("./src/fig4/gbif-key-species.R"))
fig_4 + patchwork::plot_annotation(
    caption = paste0(
        "Biodiversity infrastructure is both a foundational resource for
        long-term ecological research and an open source of real-time
        epidemic intelligence. Millions of geolocated occurrence records
        exist for major disease vectors (A: the yellow fever mosquito
        [Aedes aegypti]) and wildlife reservoirs (B: horseshoe bats
        [Rhinolophus spp.], the evolutionary reservoirs of SARS-like
        coronaviruses). Museum collections of these organisms are also an
        important resource for both fundamental biological research and viral
        discovery. (Image sources: GBIF). "
    )
)
```

### Figure from Box 2

Box two discusses data opportunities and data gaps. The figure makes use of IUCN data and data from the Virion dataset. 

```{r}
source(here::here("./src/box2/data-and-data-gaps.R"))
all_panels + patchwork::plot_annotation(
    caption = paste0(
        "Proportion of mammal species without any known viruses, by taxonomy
        (for the ten most speciose orders) and geography."
    )
)
```
